Evolutionary Algorithm for the Bonded Molecular Conformation Problem

### 2018-08-30 documentation/paper.tex
Implemented command line args

\title{3 Stage Hybrid Optimisation Algorithm for the Bonded Lennard-Jones Molecular Conformation Problem}
\author{Bennett Gale}
\date{August 2018}
\lstset{language=C++, basicstyle=\ttfamily}

@@

Genetic algorithms have been applied \cite{doi:10.1002/qua.560440214,
PULLAN1998331} successfully in order to extend the range of input size $N$ that
is reachable through structural optimisation. This population based approach
emulates the Darwinian process of natural selection, and works by performing
crossover operations on pairs of candidate configurations with selection
probabilities based on their fitness, producing new child nodes which contain
genetic material from both parents. With every crossover operation there is a
small chance of subsequent random mutation of the child configurations, the
purpose of which is to promote genetic diversity within the population and
prevent premature convergence. Over many generations the population converges
towards a global minimum as each configuration communicates information about
the global search space through the crossover operation. This method has been
successful in producing results that were previously unseen in literature for
certain input sizes \cite{PULLAN1998331}.

>>>>

\title{Evolutionary Algorithm for the Bonded Molecular Conformation Problem}
\author{Bennett Gale}
\date{August 2018}
\lstset{language=C++, basicstyle=\ttfamily}

@@

Genetic algorithms have been applied \cite{doi:10.1002/qua.560440214,
PULLAN1998331, } successfully in order to extend the range of input size $N$ that
is reachable through structural optimisation. This population based approach
emulates the Darwinian process of natural selection, and works by performing
crossover operations on pairs of candidate configurations with selection
probabilities based on their fitness, producing new child nodes which contain
genetic material from both parents. With every crossover operation there is a
small chance of subsequent random mutation of the child configurations, the
purpose of which is to promote genetic diversity within the population and
prevent premature convergence. Over many generations the population converges
towards a global minimum as each configuration communicates information about
the global search space through the crossover operation. This method has been
successful in producing results that were previously unseen in literature for
certain input sizes \cite{PULLAN1998331}.
